### 2020-09-02 README.Rmd

| Literature                           | Package    | Reference     | mlr3 Sugar                     |
|--------------------------------------|------------|---------------|--------------------------------|
| Spatial Buffering                    | blockCV    | Valavi 2019   | `rsmp("spcv-buffer")`          |
| Spatial Blocking                     | blockCV    | Valavi 2019   | `rsmp("spcv-block")`           |
| Spatial CV                           | sperrorest | Brenning 2012 | `rsmp("spcv-coords")`          |
| Environmental Blocking               | blockCV    | Valavi 2019   | `rsmp("spcv-env")`             |
| \-                                   | \-         | \-            | `rsmp("sptcv-cluto")`          |
| Leave-Location-and-Time-Out          | CAST       | Meyer 2018    | `rsmp("sptcv-cstf")`           |
| ---                                  | ---        | ---           | ---                            |
| Repeated Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-block")`  |
| Repeated Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("repeated-spcv-coords")` |
| Repeated Env Blocking                | blockCV    | Valavi 2019   | `rsmp("repeated-spcv-env")`    |
| \-                                   | \-         | \-            | `rsmp("repeated-sptcv-cluto")` |
| Repeated Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("repeated-sptcv-cstf")`  |

@@

```{r spcv-coords-all-partitions, warning=FALSE}
library(mlr3)
library(mlr3spatiotempcv)
library(ggplot2)

task = tsk("ecuador")
resampling = rsmp("spcv-coords", folds = 5)
resampling$instantiate(task)

@@

```{r spcv-coords-fold}
plot(resampling, task, fold_id = 1, crs = 4326)
```

@@

```{r spatiotemp, eval=FALSE}
library(plotly)
task_st = tsk("cookfarm")
resampling = rsmp("sptcv-cluto", folds = 5)
resampling$instantiate(task_st, time_var = "Date")
plot(resampling, task_st, fold_id = 1, point_size = 3)
```

>>>>

| Literature                           | Package    | Reference     | mlr3 Sugar                     |
|--------------------------------------|------------|---------------|--------------------------------|
| Spatial Buffering                    | blockCV    | Valavi 2019   | `rsmp("spcv_buffer")`          |
| Spatial Blocking                     | blockCV    | Valavi 2019   | `rsmp("spcv_block")`           |
| Spatial CV                           | sperrorest | Brenning 2012 | `rsmp("spcv_coords")`          |
| Environmental Blocking               | blockCV    | Valavi 2019   | `rsmp("spcv_env")`             |
| \-                                   | \-         | \-            | `rsmp("sptcv_cluto")`          |
| Leave-Location-and-Time-Out          | CAST       | Meyer 2018    | `rsmp("sptcv_cstf")`           |
| ---                                  | ---        | ---           | ---                            |
| Repeated Spatial Blocking            | blockCV    | Valavi 2019   | `rsmp("repeated_spcv_block")`  |
| Repeated Spatial CV                  | sperrorest | Brenning 2012 | `rsmp("repeated_spcv_coords")` |
| Repeated Env Blocking                | blockCV    | Valavi 2019   | `rsmp("repeated_spcv_env")`    |
| \-                                   | \-         | \-            | `rsmp("repeated_sptcv_cluto")` |
| Repeated Leave-Location-and-Time-Out | CAST       | Meyer 2018    | `rsmp("repeated_sptcv_cstf")`  |

@@

```{r spcv_coords-all-partitions, warning=FALSE}
library(mlr3)
library(mlr3spatiotempcv)
library(ggplot2)

task = tsk("ecuador")
resampling = rsmp("spcv_coords", folds = 5)
resampling$instantiate(task)

@@

```{r spcv_coords-fold}
plot(resampling, task, fold_id = 1, crs = 4326)
```

@@

```{r spatiotemp, eval=FALSE}
library(plotly)
task_st = tsk("cookfarm")
resampling = rsmp("sptcv_cluto", folds = 5)
resampling$instantiate(task_st, time_var = "Date")
plot(resampling, task_st, fold_id = 1, point_size = 3)
```
